Viability of FTIR on fossil pollen

### 2020-05-22 manuscript.Rmd
updated core segment in manus; sent to Al

Totenmoos [@heissUltenValleySouth2005]:
- bog-sediment core; past 15000 yrs
- min 1000 grains counted
- Picea, Pinus very common, switch at 10000 BP from Pinus to Picea
- Alnus, Betula throughout
- Abies, Fagus after 9000 BP
- trace Quercus

@@

Tinner alpine:

Tinner meso-mediterranean:
[@bisculmHoloceneVegetationFire2012; @vanniereClimateHumandrivenFire2008]
Quercus sections Quercus, Cerris and Ilex

Tinner sub-mediterranean:
[@zoller19601960]
Quercus sections Quercus, Cerris and Ilex

@@

# Methods and Materials 
PCA on grains for exploration

regression of spectra on depth

@@

average all spectra and stack plot

@@

>>>>

@@

Tinner/Cesar cores:
Urio Quattrocchi (supra mediterranean) [@bisculmHoloceneVegetationFire2012]
Sa Curcurica (thermo mediterranean) [@beffaVegetationFireHistory2016]
Lago del Sangiatto (southern alps)

@@

# Methods and Materials

Pollen extraction:

1. add 1 cube to vial (~1cm^-3^)
2. wash with water -> dissolve sediment vortex
3. centrifuge 3min 3000rpm
4. decant; save decant
5. add 3 ml 1.43 SPT solution
6. vortex
7. centrifuge 3min 3000rpm
8. decant supernatant into new vial
9. repeat 5-7; decant into same vial
10. wash with water; save decant for checking
11. wash with water; save decant x2
12. wash residue with water; save in vial

Preprocessing:
- SG 2nd degree, 2 poly, windowsize 5 or 6
- EMSC linear (probably needs to involve background spectra to filter them out)

PCA on grains for exploration

PLS regression of spectra on depth

@@

average all spectra and stack plots of different depth

@@

# References
